Fusion Moves for Correlation Clustering

### 2014-11-14 paper/egpaper_for_review.tex
fixed all changes until page 4 for which i knew the fix

%-------------------------------------------------------------------------
\subsection{Polyhedral Interpretation}
A polyheadral interpretation of fusion moves is shown in Fig.~\ref{fig:polyheadral}.
In each iteration the current and proposed segmentation define an inner polyheadral 
approximation of the original polytope. This interpretation holds for original 
fusion moves~\cite{Lempitsky-2010} as well as for the proposed CC-Fusion.

In our case, optimizing over the inner polytope is the same kind of problem as the original multicut polytope, but much smaller.
Furthermore, the costs does not change and and improvement in the smaller polytope will 
be the same in the original graph, as shown in Theorem~\ref{thm:Equivalence}.

>>>>

%-------------------------------------------------------------------------
\subsection{Polyhedral Interpretation}
A polyhedral interpretation of fusion moves is shown in Fig.~\ref{fig:polyheadral}.
In each iteration the current and proposed segmentation define an inner polyhedral 
approximation of the original polytope. This interpretation holds for original 
fusion moves~\cite{Lempitsky-2010} as well as for the proposed CC-Fusion.

In our case, optimizing over the inner polytope is the same kind of problem as the original multicut polytope, but much smaller.
Furthermore, the cost do not change and an improvement in the smaller polytope will 
be the same in the original graph, as shown in Theorem~\ref{thm:Equivalence}.
